---
title: "Full_reproducible_3PAD"
author: "Matilda Mikkola Jäghammar"
date: "2026-04-28"
output: html_document
---

# Setup

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
# ---------------------------
# 1. Setup
# ---------------------------
knitr::opts_chunk$set(echo = TRUE)

if (!require(pacman)) install.packages("pacman")

pacman::p_load(
  tidyverse, readxl, mice, miceadds, broom.mixed, naniar, DHARMa, AER, lmtest, ggfortify, gt, gtsummary, lmtest, MASS, dplyr, ggplot2, broom, scales, flextable, dagitty, ggdag, rms)

# ---------------------------
# 2. Load data
# ---------------------------


subset_3pad <- read_excel("3PAD/data/3PADCombined_R_allSubs_14Mar25.xlsx")

# ---------------------------
# 3. Medication construction
# ---------------------------
subset_3pad <- subset_3pad %>%
  mutate(
    meds_gb1 = if_else(
      str_detect(
        gb1_meds_annat,
        regex("Amitriptylin|Lergigan Comp|Xonvea", ignore_case = TRUE)
      ),
      1, 0
    ),
    meds_gb1 = replace_na(meds_gb1, 0),
    
SSRI_use_num = if_else(tolower(SSRI) == "yes", 1, 0, missing = 0),
meds = pmax(SSRI_use_num, meds_gb1)
  )

combined_preg <- subset_3pad %>%
  transmute(
    pid,
    age = gb1_age,
    bmi,
    
    # T1
    EPDS_T1 = gb1_epds_sum,
    GAD7_T1 = gb1_gad7_sum,
    SPDD_T1 = PAADiff / 0.1,
    IPDD_T1 = PTRDiff / 0.1,
    parity_T1 = factor(ifelse(gb1_first_preg == 1, 1, 0)),
    anemia_T1 = factor(ifelse(gb1_anemia == 1, 1, 0)),
    gest_week_T1 = gb1_preg_week,
    pss_T1 = gb1_pss_sum,
    
    # T2
    EPDS_T2 = gb2_epds_sum,
    GAD7_T2 = gb2_gad7_sum,
    SPDD_T2 = PAADiff2 / 0.1,
    IPDD_T2 = PTRDiff2 / 0.1,
    parity_T2 = factor(ifelse(gb2_first_preg == 1, 1, 0)),
    anemia_T2 = factor(ifelse(gb2_anemia == 1, 1, 0)),
    gest_week_T2 = gb2_preg_week,
    pss_T2 = gb2_pss_sum,
    SPD_Mean_T1 = PAAMean,
    IPD_Mean_T1 = PTRMean,
    PD_mean_T1 = PCUMean,
    PD_meandiff_T1 = PCUDiff,
    PD_meandiff_T2 = PCUDiff2,
    PARD_T1 = PARDiff,
    PARD_T2 = PARDiff2,
    PAR_mean_T1 = PARMean,
    PAR_mean_T2 = PARMean2,
    meds = factor(meds)
  )
# Replace the two parity lines with this single unified parity variable
combined_preg <- combined_preg %>%
  mutate(
    parity = factor(ifelse(
      is.na(parity_T1), 
      as.character(parity_T2),  # Use T2 if T1 missing
      as.character(parity_T1)   # Otherwise use T1
    ))
  ) %>%
  # Drop the old separate columns (optional)
  dplyr::select(-parity_T1, -parity_T2)

```

## **Variable list**

**T1= early pregnancy; T2 = late pregnancy**

**IPDD**\* - Initial Pupil Dilation Difference (scaled x10; numeric; IC-C difference score)

**SPDD**\*- Sustained Pupil Dilation Difference (scaled x10; numeric; IC-C difference score)

**EPDS** - Scores on Edinburgh Postnatal Depression Scale (Integer; 0-30)

**GAD7** - Scores on Generalized Anxiety Disorder-7 (Integer; 0-21)

**parity** - Multiparous/Nulliparous (factor; 1/0)

**anemia** - self reported anemia status (factor; 1 = anemic/0 = not anemic)

**age** - Maternal age (numeric; years)

**GAD_AC_T2** - Elevated anxiety scores in late pregnancy (factor; 1 ≥7, 0)

**EPDS_AC_T2** - Elevated depression scores in late pregnancy (factor; 1 ≥10, 0)

**meds** - combination of SSRI (use) and Amitriptylin, Lergigan Comp, Xonvea (factor; 1 = use/0 = don't use)

**Only included in imputation model** **as auxiliary variables**: gest_week (gestation in weeks), pss_T1 (perceived stress score), SPD_Mean (mean SPD value across both trials) IPD_Mean (mean IPD value across both trials), Other pupillary measures: PD_mean (overall pupil mean), PD_meandiff (overall pupil size mean difference), , PARD (pupil at response difference), PAR_mean (pupil at response mean),

*\* Pupil diameter difference scores, reflecting the difference between incongruent and congruent trials, were included as continuous independent variables in the negative binomial regression models. These scores, originally ranging approximately from -0.5 to 0.6, were multiplied by a factor of 10 prior to analysis. This scaling was performed to improve the interpretability of the regression coefficients, allowing for the estimation of effects associated with a 0.1-unit change in the original pupil diameter difference, which is a more physiologically meaningful and within-sample increment than a 1-unit change.*

# Inspecting variable distribution & missingness

```{r missingness, echo=FALSE, warning=FALSE, message=FALSE}
md.pattern(combined_preg, rotate.names = T)
gg_miss_var(combined_preg)
```

```{r distribution, echo=FALSE, warning=FALSE, message=FALSE}
histogram <- c("SPDD_T1", "IPDD_T1", "SPDD_T2", "IPDD_T2", "EPDS_T1", "EPDS_T2", "GAD7_T1", "GAD7_T2")

combined_preg %>%
  dplyr::select(all_of(histogram)) %>%
  pivot_longer(everything()) %>%
  ggplot(aes(x = value)) +
  geom_histogram(bins = 30) +
  facet_wrap(~name, scales = "free")

combined_preg %>%
  dplyr::select(all_of(histogram)) %>%
  pivot_longer(everything()) %>%
  ggplot(aes(x = name, y = value)) +
  geom_boxplot() +
  coord_flip()

```

## Comparing models with different distributions

Due to skewness in outcomes we compare models of different distributions and assess overdispersion

```{r comparing_models, echo=FALSE, warning=FALSE, message=FALSE}
# Gaussian
lm_mod <- lm(GAD7_T2 ~ SPDD_T2 + IPDD_T2 + parity + anemia_T2 + age + meds, data = combined_preg)

# Gassian diagnostics
bptest(lm_mod)
autoplot(lm_mod)
hist(residuals(lm_mod), breaks = 30)
shapiro.test(residuals(lm_mod))
# Deviations at the tails, significant non-normality

# Poisson
pois_mod <- glm(GAD7_T2 ~ SPDD_T2 + IPDD_T2 + parity + anemia_T2 + age + meds, data = combined_preg, family = poisson(link = "log"))

dispersiontest(pois_mod)
# Significant overdispersion 


# Negative binomial 
nb_mod <- MASS::glm.nb(GAD7_T2 ~ SPDD_T2 + IPDD_T2 + parity + anemia_T2 + age + meds, data = combined_preg)

sim <- simulateResiduals(nb_mod)
plot(sim)
testDispersion(sim)
testZeroInflation(sim)
# No significant overdispersion or zero-inflation

AIC(lm_mod, pois_mod, nb_mod)
```

- **Negative binomial seems to fit the data best (lowest AIC)**

- Improvement over Poisson is large → strong evidence of **overdispersion**

- Even compared to LM → NB still fits better

*Negative binomial regression is designed for **count data** with overdispersion, we aknowledge that these scores are composite psychometric scales rather than true event counts. NBRM provides a flexible modeling framework for overdispersed, discrete outcomes and has been widely applied in studies of depressive and anxiety symptom scores (Al Hinai & Al Hinai, 2014; Ammann et al., 2025; Clery et al., 2025; Guo et al., 2023; A. R. Huang et al., 2024; Ku et al., 2018; Wang et al., 2025; Zhang et al., 2023)*

# Descriptives: Table 1

```{r table_1, echo=FALSE, warning=FALSE, message=FALSE}
# =============================================================================
# TABLE 1 CODE 
# =============================================================================

table_1 <- subset_3pad %>%
  transmute(
    pid,
    age = gb1_age,
    bmi,

    education = factor(if_else(edu == "University", "University", "Lower")),
    country   = factor(if_else(country == "Sweden", "Sweden", "Other")),

    # Binary variables (CLEAN YES/NO STANDARD)
    Medication = factor(if_else(meds == 1, "Yes", "No")),
    SSRI       = factor(if_else(SSRI == "Yes", "Yes", "No")),
    PCOS       = factor(if_else(pcos == "Yes", "Yes", "No")),

    # T1 outcomes
    EPDS_T1 = gb1_epds_sum,
    GAD7_T1 = gb1_gad7_sum,

    parity_T1 = factor(if_else(gb1_first_preg == 1, "Nulliparous", "Multiparous")),
    anemia_T1 = factor(if_else(gb1_anemia == 1, "Anemic", "Not anemic")),

    gest_week_T1 = as.numeric(gb1_preg_week),

    relationship_status_T1 = factor(if_else(gb1_relationship == 1, "Yes", "No")),

    exercise_T1 = factor(if_else(exercise1 == "Moderate to high",
                                 "Moderate to high", "Low to none")),

    pos_LE1 = factor(if_else(pos_LE1 == "Yes", "Yes", "No")),
    neg_LE1 = factor(if_else(neg_LE1 == "Yes", "Yes", "No")),

    # T2 outcomes
    EPDS_T2 = gb2_epds_sum,
    GAD7_T2 = gb2_gad7_sum,

    parity_T2 = factor(if_else(gb2_first_preg == 1, "Nulliparous", "Multiparous")),
    Anemia_T2 = factor(if_else(gb2_anemia == 1, "Anemic", "Not anemic")),

    gest_week_T2 = as.numeric(gb2_preg_week),

    neg_LE2 = factor(if_else(neg_LE2 == "Yes", "Yes", "No")),
    pos_LE2 = factor(if_else(pos_LE2 == "Yes", "Yes", "No"))
  )

table_1 <- table_1 %>%
  mutate(
    Parity = factor(if_else(
      is.na(parity_T1),
      as.character(parity_T2),
      as.character(parity_T1)
    ))
  ) %>%
  dplyr::select(-parity_T1, -parity_T2)

table_1 <- table_1 %>%
  mutate(
    GAD_high_T1  = factor(if_else(GAD7_T1  >= 7,  "High", "Low")),
    EPDS_high_T1 = factor(if_else(EPDS_T1 >= 10, "High", "Low")),
    GAD_high_T2  = factor(if_else(GAD7_T2  >= 7,  "High", "Low")),
    EPDS_high_T2 = factor(if_else(EPDS_T2 >= 10, "High", "Low"))
  )

table_1_T1 <- table_1 %>% 
  dplyr::select(-EPDS_high_T2, -GAD_high_T2, -Anemia_T2, -neg_LE2, -pos_LE2, -gest_week_T2)

table_1_T2 <- table_1 %>% 
  dplyr::select(pid, EPDS_high_T2, GAD_high_T2, Anemia_T2, neg_LE2, pos_LE2, gest_week_T2, EPDS_T2, GAD7_T2)


t1_epds <- table_1_T1 %>%
  dplyr::select(-pid, -GAD_high_T1) %>%

  tbl_summary(
    by = EPDS_high_T1,
    type = c(gest_week_T1, bmi, EPDS_T1, EPDS_T2, GAD7_T1, GAD7_T2, age) ~ "continuous",
    missing = "ifany",
    missing_text = "Missing",
    sort = all_categorical() ~ "frequency",
    statistic = all_continuous() ~ "{mean} ({sd})",
    digits = all_categorical() ~ 1,
    label = list(
      relationship_status_T1 ~ "In a relationship",
      exercise_T1 ~ "Exercise level",
      anemia_T1 ~ "Self-reported anemia (T1)",
      country ~ "Country of birth",
      age ~ "Maternal age",
      gest_week_T1 ~ "Gestational week (T1)",
      education ~ "Educational attainment",
      pos_LE1 ~ "Recent positive life events (T1)",
      neg_LE1 ~ "Recent negative life events (T1)",
      EPDS_T1 ~ "EPDS score (T1)",
      GAD7_T1 ~ "GAD7 score (T1)",
      EPDS_T2 ~ "EPDS score (T2)",
      GAD7_T2 ~ "GAD7 score (T2)",
      bmi ~ "BMI"
    )
  ) %>%

  modify_header(
    stat_1 ~ "**High (≥10)**",
    stat_2 ~ "**Low (<10)**"
  ) %>%
  modify_spanning_header(update = all_stat_cols() ~ "**EPDS score**") %>% 

  add_overall() %>%
  bold_labels() %>%
  italicize_levels()


t2_epds <- table_1_T2 %>%
  dplyr::select(-pid, -GAD_high_T2) %>%
  tbl_summary(
    by = EPDS_high_T2,
    missing = "ifany",
    missing_text = "Missing",
    sort = all_categorical() ~ "frequency",
    type = c(gest_week_T2, EPDS_T2, GAD7_T2) ~ "continuous",
    statistic = all_continuous() ~ "{mean} ({sd})",
    digits = all_categorical() ~ 1,
      label =  list(gest_week_T2 ~ "Gestational week (T2)", 
pos_LE2 ~ "Recent positive life events (T2)",
neg_LE2 ~ "Recent negative life events (T2)",
Anemia_T2 ~ "Self reported anemia (T2)", EPDS_T2 ~ "EPDS score (T2)",
      GAD7_T2 ~ "GAD7 score (T2)")) %>%
  add_overall() %>% 
  bold_labels() %>% 
  italicize_levels()

t_epds <- tbl_stack(list(t1_epds, t2_epds), group_header = c("T1", "T2"))

t1_gad <- table_1_T1 %>%
  dplyr::select(-pid, -EPDS_high_T1) %>%

  tbl_summary(
    by = GAD_high_T1,
    type = c(gest_week_T1, bmi, EPDS_T1, EPDS_T2, GAD7_T1, GAD7_T2, age) ~ "continuous",
    sort = all_categorical() ~ "frequency",
    missing = "ifany",
    missing_text = "Missing",
    statistic = all_continuous() ~ "{mean} ({sd})",
    digits = all_categorical() ~ 1,
    label = list(
      relationship_status_T1 ~ "In a relationship",
      exercise_T1 ~ "Exercise level",
      anemia_T1 ~ "Self-reported anemia (T1)",
      country ~ "Country of birth",
      age ~ "Maternal age",
      gest_week_T1 ~ "Gestational week (T1)",
      education ~ "Educational attainment",
      pos_LE1 ~ "Recent positive life events (T1)",
      neg_LE1 ~ "Recent negative life events (T1)",
      EPDS_T1 ~ "EPDS score (T1)",
      GAD7_T1 ~ "GAD7 score (T1)",
      EPDS_T2 ~ "EPDS score (T2)",
      GAD7_T2 ~ "GAD7 score (T2)",
      bmi ~ "BMI"
    )
  ) %>%

  modify_header(
    stat_1 ~ "**High (≥7)**",
    stat_2 ~ "**Low (<7)**"
  ) %>%
  modify_spanning_header(update = all_stat_cols() ~ "**GAD7 score**") %>% 
  bold_labels() %>%
  italicize_levels() 



t2_gad <- table_1_T2 %>%
  dplyr::select(-pid, -EPDS_high_T2) %>%
  tbl_summary(
    by = GAD_high_T2,
    missing = "ifany",
    missing_text = "Missing",
    sort = all_categorical() ~ "frequency",
    type = c(gest_week_T2, EPDS_T2, GAD7_T2) ~ "continuous",
    statistic = all_continuous() ~ "{mean} ({sd})",
    digits = all_categorical() ~ 1,
      label =  list(gest_week_T2 ~ "Gestational week (T2)", 
pos_LE2 ~ "Recent positive life events (T2)",
neg_LE2 ~ "Recent negative life events (T2)",
Anemia_T2 ~ "Self-reported anemia (T2)", EPDS_T2 ~ "EPDS score (T2)",
      GAD7_T2 ~ "GAD7 score (T2)"))%>%
  bold_labels() %>% 
  italicize_levels() 

t1_table <- tbl_merge(list(t1_epds, t1_gad), tab_spanner = c("**EPDS score**", "**GAD7 score**"))
t2_table <- tbl_merge(list(t2_epds, t2_gad))

full_table <- tbl_stack(list(t1_table, t2_table), group_header = c("T1", "T2"))


full_table %>%
  as_gt()

full_table %>%
  as_flex_table() %>%
  autofit() %>%             
  flextable::save_as_docx(path = "table1.docx")
```

# Directed Acyclic Graph (DAG)

```{r DAG, echo=FALSE, message=FALSE, warning=FALSE}
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

dag <- grViz("
digraph DAG {

  graph [
    layout    = neato,
    bgcolor   = 'white',
    fontname  = 'Helvetica'
  ]

  node [
    shape    = rectangle,
    style    = 'filled,rounded',
    fontname = 'Helvetica',
    fontsize = 11,
    penwidth = 0.5,
    margin   = '0.18,0.10',
    height   = 0.45
  ]

  edge [
    arrowsize = 0.5,
    penwidth  = 0.7,
    arrowhead = vee
  ]

  # ── Exposure and outcome (middle row) ──────────────────────────────────────
  pupil [label = 'Pupil indices\n(Exposure)',
         fillcolor = '#E8EEF4', fontcolor = '#1C3A52', color = '#7A9BB5',
         pos = '1,2!']

  mh    [label = 'Symptoms of antenatal anxiety and/or depression\n(Outcome)',
         fillcolor = '#EAE8F2', fontcolor = '#2B1F4A', color = '#8A82B8',
         pos = '5,2!']

  # ── Key covariates (top row, above exposure+outcome) ───────────────────────
  age    [label = 'Age',                fillcolor = '#E6F2EC', fontcolor = '#1A3D2B', color = '#6BA888', pos = '0,5!']
  parity [label = 'Parity',             fillcolor = '#E6F2EC', fontcolor = '#1A3D2B', color = '#6BA888', pos = '2,5!']
  ssri   [label = 'SSRI / medications', fillcolor = '#E6F2EC', fontcolor = '#1A3D2B', color = '#6BA888', pos = '4,5!']
  anemia [label = 'Anemia',             fillcolor = '#E6F2EC', fontcolor = '#1A3D2B', color = '#6BA888', pos = '6,5!']

  # ── Potential covariates (right column) ────────────────────────────────────
  gest    [label = 'Gestational week',  fillcolor = '#F4F3F0', fontcolor = '#3D3B35', color = '#AAAAAA', pos = '8.5,6!']
  bmi     [label = 'BMI',              fillcolor = '#F4F3F0', fontcolor = '#3D3B35', color = '#AAAAAA', pos = '8.5,4.8!']
  edu     [label = 'Education',         fillcolor = '#F4F3F0', fontcolor = '#3D3B35', color = '#AAAAAA', pos = '8.5,3.6!']
  country [label = 'Country',           fillcolor = '#F4F3F0', fontcolor = '#3D3B35', color = '#AAAAAA', pos = '8.5,2.4!']
  life    [label = 'Life events',       fillcolor = '#F4F3F0', fontcolor = '#3D3B35', color = '#AAAAAA', pos = '8.5,1.2!']
  activ   [label = 'Physical activity', fillcolor = '#F4F3F0', fontcolor = '#3D3B35', color = '#AAAAAA', pos = '8.5,0!']

  # ── Main causal path ───────────────────────────────────────────────────────
  pupil -> mh [color = '#333333', penwidth = 1.8, arrowsize = 0.7, arrowhead = normal]

  # ── Key covariates → both nodes ────────────────────────────────────────────
  age    -> pupil [color = '#6BA888']
  age    -> mh    [color = '#6BA888']
  parity -> pupil [color = '#6BA888']
  parity -> mh    [color = '#6BA888']
  ssri   -> pupil [color = '#6BA888']
  ssri   -> mh    [color = '#6BA888']
  anemia -> pupil [color = '#6BA888']
  anemia -> mh    [color = '#6BA888']

  # ── Potential covariates → outcome only ────────────────────────────────────
  gest    -> mh [style = dashed, color = '#BBBBBB']
  bmi     -> mh [style = dashed, color = '#BBBBBB']
  edu     -> mh [style = dashed, color = '#BBBBBB']
  country -> mh [style = dashed, color = '#BBBBBB']
  life    -> mh [style = dashed, color = '#BBBBBB']
  activ   -> mh [style = dashed, color = '#BBBBBB']
}
")

svg_raw <- charToRaw(export_svg(dag))
rsvg_pdf(svg_raw, file = "dag_final.pdf")
rsvg_png(svg_raw, file = "dag_final.png", width = 2400)

dag
```

# Descriptives and Stroop effects

> The pupil measures **Initial Pupil Dilation Difference (IPDD)** and **Sustained Pupil Dilation Difference (SPDD)** represent differences in pupil diameter between incongruent and congruent trials (IC-C).
>
> The behavioral measures **Accuracy** and **RT (response time)** represent differences in % of accurate button presses and differences in response time (IC-C)
>
> If mu = 0, there is no significant difference between trial types

```{r descriptives, echo=FALSE, warning=FALSE, message=FALSE}
EST_measures <- subset_3pad %>% 
  transmute(SPDD_T1 = PAADiff,
    IPDD_T1 = PTRDiff, accuracy_T1 = AccDiff, RT_T1 = RTDiff, SPDD_T2 = PAADiff2,
    IPDD_T2 = PTRDiff2, accuracy_T2 = AccDiff2, RT_T2 = RTDiff2)

#Check assumptions for parametric one-sample t-test
# Pupil measures
shapiro.test(EST_measures$IPDD_T1)
shapiro.test(EST_measures$SPDD_T1)
shapiro.test(EST_measures$SPDD_T2)
shapiro.test(EST_measures$IPDD_T2)

# Behavioral measures
shapiro.test(EST_measures$accuracy_T1)
shapiro.test(EST_measures$RT_T1)
shapiro.test(EST_measures$accuracy_T2)
shapiro.test(EST_measures$RT_T2)


# Define both
my_wilcox <- function(data, variable, ...) {
  wilcox.test(data[[variable]], mu = 0)$p.value
}

my_ttest <- function(data, variable, ...) {
  t.test(data[[variable]], mu = 0)$p.value
}

# Apply selectively
est_tbl <- EST_measures %>%
  tbl_summary(statistic = all_continuous() ~ "{mean} ({sd}) {min} {max}", missing = "no",
    missing_text = "Missing", label = list(accuracy_T1 ~ "Accuracy (T1)", accuracy_T2 ~ "Accuracy (T2)", RT_T1 ~ "Response time (T1)", RT_T2 ~ "Response time (T2)", SPDD_T1 ~ "SPDD (T1)", SPDD_T2 ~ "SPDD (T2)", IPDD_T1 ~ "IPDD (T1)", IPDD_T2 ~ "IPDD (T2)")
) %>%
  add_stat(
    fns = list(
      c("accuracy_T1", "accuracy_T2", "RT_T2") ~ my_wilcox,
      c("IPDD_T2", "SPDD_T2", "IPDD_T1", "SPDD_T1", "RT_T1") ~ my_ttest)) %>% 
  modify_header(add_stat_1 ~ "**P-value**")


est_tbl %>%
  as_flex_table() %>%
  save_as_docx(path = "stroop.docx")
```

```{r descriptives_outcomes, echo=FALSE}
out_measures <- subset_3pad %>% 
  transmute(EPDS_T1 = gb1_epds_sum,
    EPDS_T2 = gb2_epds_sum, GAD_T2 = gb2_gad7_sum,
    GAD_T1 = gb1_gad7_sum)

out_measures <- out_measures %>%
  mutate(
    GAD_high_T1  = factor(if_else(GAD_T1  >= 7,  "High", "Low")),
    EPDS_high_T1 = factor(if_else(EPDS_T1 >= 10, "High", "Low")),
    GAD_high_T2  = factor(if_else(GAD_T2  >= 7,  "High", "Low")),
    EPDS_high_T2 = factor(if_else(EPDS_T2 >= 10, "High", "Low"))
  )

gad_group_t2 <- table(out_measures$GAD_high_T2)
gad_group_t1 <- table(out_measures$GAD_high_T1)
epds_group_t1 <- table(out_measures$EPDS_high_T1)
epds_group_t2 <- table(out_measures$EPDS_high_T2)

```

At T1 GAD-7 (high, low) = `r gad_group_t1` and EPDS = `r epds_group_t1`

At T2 GAD-7 = `r gad_group_t2` and EPDS = `r epds_group_t2`

# Imputation

Missing data (13% overall) can bias results and reduce power under complete-case analysis (Dettori et al., 2018). Data were therefore assumed missing at random (MAR) conditional on observed covariates and handled via multiple imputation by chained equations (MICE; m=30, 15 iterations).

```{r imputation, echo=FALSE, warning=FALSE, message=FALSE}
# Initialize mice
ini  <- mice(combined_preg, maxit = 0, printFlag = FALSE)
meth <- ini$method
pred <- ini$predictorMatrix
post <- ini$post

# Structure variable types
base_covars <- c("age", "parity", "anemia_T1", "meds", "bmi", "gest_week_T1", "pss_T1", "SPD_Mean_T1", "IPD_Mean_T1", "PAR_mean_T1",
  "PD_mean_T1","PD_meandiff_T1")  
t2_covars <- c("age", "parity", "anemia_T1", "meds", "bmi", "gest_week_T2", "pss_T2", "PD_meandiff_T2","PARD_T1","PARD_T2", "PAR_mean_T2")  
t1_vars <- c("EPDS_T1", "GAD7_T1", "IPDD_T1", "SPDD_T1")  

# Decide predictor matrices, perserving temporal structure
pred["EPDS_T1", c(base_covars, "GAD7_T1", "IPDD_T1", "SPDD_T1")] <- 1 
pred["GAD7_T1", c(base_covars, "EPDS_T1", "IPDD_T1", "SPDD_T1")] <- 1  
pred["IPDD_T1", c(base_covars, "EPDS_T1", "GAD7_T1", "SPDD_T1")] <- 1 
pred["SPDD_T1", c(base_covars, "EPDS_T1", "GAD7_T1", "IPDD_T1")] <- 1  

pred["EPDS_T2", ] <- 0
pred["EPDS_T2", c(base_covars, t1_vars)] <- 1

pred["GAD7_T2", ] <- 0
pred["GAD7_T2", c(base_covars, t1_vars)] <- 1

pred["IPDD_T2", ] <- 0
pred["IPDD_T2", c(base_covars, t1_vars)] <- 1

pred["SPDD_T2", ] <- 0
pred["SPDD_T2", c(base_covars, t1_vars)] <- 1

# Don't impute participant id
no_impute <- c("pid")

pred[no_impute, ] <- 0            
bin_vars <- c("anemia_T1", "anemia_T2",
              "parity",
              "meds")

bin_vars <- bin_vars[!(bin_vars %in% no_impute)]
meth[bin_vars] <- "logreg" # binary variables use logistic regression with bootstrapping

# Then run mice
imp <- mice(
  data            = combined_preg,
  m               = 30,
  method          = meth,           
  predictorMatrix = pred,
  post            = post,
  maxit           = 10,
  seed            = 555, 
  printFlag       = FALSE
)
imp$method # Check correct methods (pmm for continous)
plot(imp) # Visualize imputation patterns
```

# Cross-sectional modelling

In this section we will answer *RQ1: Examine cross-sectional associations between pupil indices and psychological symptom severity (EPDS, GAD-7) in early (T1) and late (T2) pregnancy.*

At each timepoint we will conduct generalized linear models with a negative binomial distribution to estimate associations between pupil indices and symptom scores, adjusting for relevant covariates. GAD-7 and EPDS will be modeled as separate outcomes with two models at each timepoint (unadjusted = main exposures only, adjusted = adjusted for age, parity, anemia status and medication use)

```{r cross_models, echo=FALSE, warning=FALSE, message=FALSE}

# EPDS T1
# Unadjusted
epds_t1_unadj <- with(
  imp,
  glm.nb(EPDS_T1 ~ SPDD_T1 + IPDD_T1)
)
# Adjusted
epds_t1_adj <- with(
  imp,
  glm.nb(EPDS_T1 ~ SPDD_T1 + IPDD_T1 + age + parity + anemia_T1 + meds)
)


# GAD7 T1
# Unadjusted
gad_t1_unadj <- with(
  imp,
  glm.nb(GAD7_T1 ~ SPDD_T1 + IPDD_T1)
)
# Adjusted
gad_t1_adj <- with(
  imp,
  glm.nb(GAD7_T1 ~ SPDD_T1 + IPDD_T1 + age + parity + anemia_T1 + meds)
)

#EPDS T2
# Unadjusted
epds_t2_unadj <- with(
  imp,
  glm.nb(EPDS_T2 ~ SPDD_T2 + IPDD_T2)
)
# Adjusted
epds_t2_adj <- with(
  imp,
  glm.nb(EPDS_T2 ~ SPDD_T2 + IPDD_T2 + age + parity + anemia_T2 + meds)
)

# GAD7 T2
# Unadjusted
gad_t2_unadj <- with(
  imp,
  glm.nb(GAD7_T2 ~ SPDD_T2 + IPDD_T2)
)

# Adjusted
gad_t2_adj <- with(
  imp,
  glm.nb(GAD7_T2 ~ SPDD_T2 + IPDD_T2 + age + parity + anemia_T2 + meds)
)
```

## Model comparisons

Model comparisons were conducted using both D1 (pooled Wald) and D2 (likelihood-based) tests to ensure robustness under multiple imputation

```{r model comparisons, echo=FALSE}
D1(gad_t2_adj, gad_t2_unadj)
D1(gad_t1_adj, gad_t1_unadj)
D1(epds_t1_adj, epds_t1_unadj)
D1(epds_t2_adj, epds_t2_unadj)


D2(gad_t2_adj, gad_t2_unadj)
D2(gad_t1_adj, gad_t1_unadj)
D2(epds_t1_adj, epds_t1_unadj)
D2(epds_t2_adj, epds_t2_unadj)
```

gad_t2: Both pooled Wald (D1) and likelihood-based (D2) tests indicated that the adjusted model provided a significantly better fit than the unadjusted model (all p \< .05).

gad_t1: There was no evidence that the adjusted model improved fit over the unadjusted model, D1: F(4, 89.9) = 0.34, p = .848; D2: F(4, …) = 0.37, p = .828.

epds_t1: There was no evidence that the adjusted model improved fit for EPDS at T1 (D1: F(4, 90.0) = 0.53, p = .713; D2: F(4, …) = 0.49, p = .742).

epds_t2: There was no evidence that the adjusted model improved fit for EPDS at T2 (D1: F(4, 89.1) = 1.17, p = .329; D2: F(4, …) = 1.23, p = .295).

## Checking assumptions and diagnostics

```{r model_diagnostics, echo=FALSE, warning=FALSE, message=FALSE}
#T1

model_list <- gad_t1_adj$analyses
model_list2 <- gad_t1_unadj$analyses

# 2. Calculate AIC for each model
aic_adj <- sapply(model_list, AIC)
aic_unadj <- sapply(model_list2, AIC)

# 3. Mean AIC
mean(aic_adj)
mean(aic_unadj)

# Residual check on the first imputed dataset
sim_res <- simulateResiduals(model_list[[1]])
plot(sim_res)

sim_res <- simulateResiduals(model_list2[[1]])
plot(sim_res)

#T2 
# 1. Extract the list of models
model_list <- gad_t2_adj$analyses
model_list2 <- gad_t2_unadj$analyses

# 2. Calculate AIC for each model
aic_adj <- sapply(model_list, AIC)
aic_unadj <- sapply(model_list2, AIC)

# 3. Mean AIC
mean(aic_adj)
mean(aic_unadj)

# Residual check on the first imputed dataset
sim_res <- simulateResiduals(model_list[[1]])
plot(sim_res)

sim_res <- simulateResiduals(model_list2[[1]])
plot(sim_res)


# 1. Extract one imputed dataset
#T1

model_list <- epds_t1_adj$analyses
model_list2 <- epds_t1_unadj$analyses

# 2. Calculate AIC for each model
aic_adj <- sapply(model_list, AIC)
aic_unadj <- sapply(model_list2, AIC)

# 3. Mean AIC
mean(aic_adj)
mean(aic_unadj)

# Residual check on the first imputed dataset
sim_res <- simulateResiduals(model_list[[1]])
plot(sim_res)

sim_res <- simulateResiduals(model_list2[[1]])
plot(sim_res)


# Check if model specification is correct 
# 1. Extract one imputed dataset

#T2 
# 1. Extract the list of models
model_list <- epds_t2_adj$analyses
model_list2 <- epds_t2_unadj$analyses

# 2. Calculate AIC for each model
aic_adj <- sapply(model_list, AIC)
aic_unadj <- sapply(model_list2, AIC)

# 3. Mean AIC
mean(aic_adj)
mean(aic_unadj)

# Residual check on the first imputed dataset
sim_res <- simulateResiduals(model_list[[1]])
plot(sim_res)

sim_res <- simulateResiduals(model_list2[[1]])
plot(sim_res)
```

## Regression tables

```{r tables, echo=FALSE, warning=FALSE, message=FALSE}
#T1 GAD Table
gad_t1_unadj_table <- tbl_regression(gad_t1_unadj, exponentiate = T, label =  list(SPDD_T1 ~ "SPDD (T1)", IPDD_T1 ~ "IPDD (T1)")) %>% bold_labels() %>% 
  italicize_levels() 
  
gad_t1_adj_table<- tbl_regression(gad_t1_adj, exponentiate = T, include = c(SPDD_T1, IPDD_T1), label =  list(SPDD_T1 ~ "SPDD (T1)", IPDD_T1 ~ "IPDD (T1)"))  %>% bold_labels() %>% 
  italicize_levels() 

tbl_gad_t1 <- tbl_merge(list(gad_t1_unadj_table, gad_t1_adj_table), tab_spanner = c("**Unadjusted**", "**Adjusted**"))


# T2 GAD Table
gad_t2_unadj_table <- tbl_regression(gad_t2_unadj, exponentiate = T, label =  list(SPDD_T2 ~ "SPDD (T2)", IPDD_T2 ~ "IPDD (T2)")) %>% bold_labels() %>% 
  italicize_levels() 
  
gad_t2_adj_table<- tbl_regression(gad_t2_adj, exponentiate = T, include = c(SPDD_T2, IPDD_T2), label =  list(SPDD_T2 ~ "SPDD (T2)", IPDD_T2 ~ "IPDD (T2)"))  %>% bold_labels() %>% 
  italicize_levels() 

tbl_gad_t2 <- tbl_merge(list(gad_t2_unadj_table, gad_t2_adj_table), tab_spanner = c("**Unadjusted**", "**Adjusted**"))


#T1 EPDS Table
epds_t1_unadj_table <- tbl_regression(epds_t1_unadj, exponentiate = T, label =  list(SPDD_T1 ~ "SPDD (T1)", IPDD_T1 ~ "IPDD (T1)")) %>% bold_labels() %>% 
  italicize_levels() 
  
epds_t1_adj_table<- tbl_regression(epds_t1_adj, exponentiate = T, include = c(SPDD_T1, IPDD_T1), label =  list(SPDD_T1 ~ "SPDD (T1)", IPDD_T1 ~ "IPDD (T1)"))  %>% bold_labels() %>% italicize_levels() 

tbl_epds_t1 <- tbl_merge(list(epds_t1_unadj_table, epds_t1_adj_table), tab_spanner = c("**Unadjusted**", "**Adjusted**"))


# T2 EPDS Table
epds_t2_unadj_table <- tbl_regression(epds_t2_unadj, exponentiate = T, label =  list(SPDD_T2 ~ "SPDD (T2)", IPDD_T2 ~ "IPDD (T2)")) %>% bold_labels() %>% 
  italicize_levels()
  
epds_t2_adj_table<- tbl_regression(epds_t2_adj, exponentiate = T, include = c(SPDD_T2, IPDD_T2), label =  list(SPDD_T2 ~ "SPDD (T2)", IPDD_T2 ~ "IPDD (T2)"))  %>% bold_labels() %>% 
  italicize_levels() %>% add_glance_source_note() 


tbl_epds_t2 <- tbl_merge(list(epds_t2_unadj_table, epds_t2_adj_table), tab_spanner = c("**Unadjusted**", "**Adjusted**"))

```

```{r stacking tables, echo=FALSE, warning=FALSE, message=FALSE}

tbl_t1 <- tbl_stack(list(tbl_gad_t1, tbl_epds_t1), group_header = c("GAD-7 (T1)", "EPDS (T1)"))

tbl_t2 <- tbl_stack(list(tbl_gad_t2, tbl_epds_t2), group_header = c("GAD-7 (T2)", "EPDS (T2)"))

tbl_cross <- tbl_stack(list(tbl_t1, tbl_t2))

tbl_cross <- tbl_cross %>% modify_header(c(groupname_col ~ "**Outcome**", label ~ "**Exposure**"))

show_header_names(tbl_cross)

tbl_cross %>%
  as_flex_table() %>%
  save_as_docx(path = "tbl_cross.docx")

tbl_cross
```

At T1 Anxiety was marginally significantly positively associated with SPDD both in the unadjusted (`r inline_text(gad_t1_unadj_table, variable = SPDD_T1)`) and the adjusted (`r inline_text(gad_t1_adj_table, variable = SPDD_T1)` model. The same pattern emerged for EPDS (unadj = `r inline_text(epds_t1_unadj_table, variable = SPDD_T1)`, adj = `r inline_text(epds_t1_adj_table, variable = SPDD_T1)`). IPDD was not associated with any of the outcomes. At T2 neither SPDD or IPDD was associated with EPDS. SPDD was inversely, marginally associated with anxiety in the unadjusted model (`r inline_text(gad_t2_unadj_table, variable = SPDD_T2)` ), and reached significance in the adjusted model (`r inline_text(gad_t2_adj_table, variable = SPDD_T2)`). Higher SPDD at T2 was associated with 12 % less concurrent symptom scores of GAD-7, suggesting a protective effect.

## Visualizing SPDD direction change

```{r visualizing_SPDD_GAD, echo=FALSE, warning=FALSE, message=FALSE}

get_spdd <- function(fit, term_label, timepoint, model_type) {
  pooled <- pool(fit)
  tidy(pooled, conf.int = TRUE, exponentiate = TRUE) %>%
    filter(term == term_label) %>%
    mutate(
      timepoint = factor(timepoint, levels = c("T1", "T2")),
      model_type = factor(model_type, levels = c("Unadjusted", "Adjusted"))
    )
}

gad_spdd <- bind_rows(
  get_spdd(gad_t1_unadj, "SPDD_T1", "T1", "Unadjusted"),
  get_spdd(gad_t1_adj,   "SPDD_T1", "T1", "Adjusted"),
  get_spdd(gad_t2_unadj, "SPDD_T2", "T2", "Unadjusted"),
  get_spdd(gad_t2_adj,   "SPDD_T2", "T2", "Adjusted")
)

pd <- position_dodge(width = 0.25)

p_gad <- ggplot(gad_spdd, aes(x = timepoint, y = estimate, color = model_type, group = model_type)) +
  geom_hline(yintercept = 1, linetype = "dashed", linewidth = 0.6, color = "grey45") +
  geom_line(linewidth = 0.8, position = pd) +
  geom_point(size = 2.8, position = pd) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    width = 0.08,
    linewidth = 0.7,
    position = pd
  ) +
  scale_y_log10(
    breaks = c(0.5, 0.75, 1, 1.25, 1.5),
    labels = number_format(accuracy = 0.01)
  ) +
  scale_color_manual(values = c("Unadjusted" = "#1c9099", "Adjusted" = "#a6bddb")) +
  labs(
    x = NULL,
    y = "Incidence rate ratio for SPDD",
    color = NULL) +
  theme_classic(base_size = 13) +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 11),
    axis.text = element_text(color = "black"),
    axis.title.y = element_text(margin = margin(r = 8)),
    plot.subtitle = element_text(size = 11, color = "grey20"),
    plot.margin = margin(8, 8, 8, 8)
  )

ggsave(
  filename = "GAD_SPDD.tiff",
  plot = p_gad,
  width = 6,
  height = 4,
  units = "in",
  dpi = 600,
  compression = "lzw"
)

p_gad
```

**Figure [X].** Illustration of the sign change of SPDD across timepoints. Unadjusted and Adjusted incidence rate ratios for SPDD and concurrent symptoms of anxiety. Estimates are from negative binomial regression models, with 95% confidence intervals indicated by vertical bars. Reference line at OR = 1 indicates null effect.

# Prospective modelling

In this section our aim was was to prospectively predict symptoms above thresholds from baseline to follow up (GAD≥7 and EPDS≥10) answering RQ2: *Examine whether pupil indices at T1 prospectively predict clinically elevated symptoms at T2.*

Models were originally intended to be adjusted for all baseline covariates and prior symptom levels. However, due to the sparse number of events for both outcomes and the presence of binary covariates (medication use, anemia, and parity), these variables yielded unstable estimates and were therefore excluded from the models; a more parsimonious approach was prioritized. The fully adjusted models therefore include only age and baseline symptom scores.

```{r models_prospective, echo=FALSE, warning=FALSE, message=FALSE}

# GAD-7 ≥ 7 at T2 and pupil measures at T1
gad_pros <- with(imp, glm(GAD7_T2 >= 7 ~ IPDD_T1 + SPDD_T1 + age + GAD7_T1, family = binomial))

# EPDS ≥ 10 at T2 and pupil measures at T1

epds_pros <- with(imp, glm(EPDS_T2 >= 10 ~ IPDD_T1 + SPDD_T1 + age + EPDS_T1, family = binomial))
```

## **Imputation‑adjusted pseudo‑R²**

```{r pseudo_r_pros, echo=FALSE}
# Unadjusted models:
# For GAD‑7 ≥ 7 at T2
gad_lrm <- fit.mult.impute(
  GAD7_T2 >= 7 ~ IPDD_T1 + SPDD_T1,
  fitter = lrm,
  xtrans = imp,          # your mice::mids object
  data = combined_preg,      # original data frame
  lrt = TRUE,            # compute LR tests on each and stacked data
  pr = FALSE
)

# For EPDS ≥ 10 at T2
epds_lrm <- fit.mult.impute(
  EPDS_T2 >= 10 ~ IPDD_T1 + SPDD_T1,
  fitter = lrm,
  xtrans = imp,
  data = combined_preg,
  lrt = TRUE,
  pr = FALSE
)

library(rms)


# GAD‑7 model
gad_as <- processMI(gad_lrm, which = "anova")

total_lr_chi2_gad <- gad_as[grepl("TOTAL", rownames(gad_as)), "Chi-Square"]

# EPDS model
epds_as <- processMI(epds_lrm, which = "anova")
total_lr_chi2_epds <- epds_as[grepl("TOTAL", rownames(epds_as)), "Chi-Square"]

n_obs <- 99

# GAD‑7 model
pseudo_R2_gad_unadj <- 1 - exp(-total_lr_chi2_gad / n_obs)

# EPDS model
pseudo_R2_epds_unadj <- 1 - exp(-total_lr_chi2_epds / n_obs)

pseudo_R2_gad_unadj   # for GAD‑7 ≥ 7 at T2
pseudo_R2_epds_unadj  # for EPDS ≥ 10 at T2

# Adjusted models: 

gad_lrm <- fit.mult.impute(
  GAD7_T2 >= 7 ~ IPDD_T1 + SPDD_T1 + age + GAD7_T1,
  fitter = lrm,
  xtrans = imp,          
  data = combined_preg,      
  lrt = TRUE,            # compute LR tests on each and stacked data
  pr = FALSE
)

# For EPDS ≥ 10 at T2
epds_lrm <- fit.mult.impute(
  EPDS_T2 >= 10 ~ IPDD_T1 + SPDD_T1 + age + EPDS_T1,
  fitter = lrm,
  xtrans = imp,
  data = combined_preg,
  lrt = TRUE,
  pr = FALSE
)

library(rms)

# GAD‑7 model
gad_as <- processMI(gad_lrm, which = "anova")

total_lr_chi2_gad <- gad_as[grepl("TOTAL", rownames(gad_as)), "Chi-Square"]

# EPDS model
epds_as <- processMI(epds_lrm, which = "anova")
total_lr_chi2_epds <- epds_as[grepl("TOTAL", rownames(epds_as)), "Chi-Square"]

n_obs <- 99

# GAD‑7 model
pseudo_R2_gad_adj <- 1 - exp(-total_lr_chi2_gad / n_obs)

# EPDS model
pseudo_R2_epds_adj <- 1 - exp(-total_lr_chi2_epds / n_obs)

pseudo_R2_gad_adj   # for GAD‑7 ≥ 7 at T2
pseudo_R2_epds_adj  # for EPDS ≥ 10 at T2
```

For the GAD‑7 ≥ 7 at T2 outcome, the imputation‑adjusted pseudo‑R² was `r round(pseudo_R2_gad_unadj, 3)` when including only pupil‑derived measures (IPDD_T1 and SPDD_T1), rising to `r round(pseudo_R2_gad_adj, 3)` when age and baseline GAD‑7 scores (GAD7_T1) were added.

For the EPDS ≥ 10 at T2 outcome, the pseudo‑R² was `r round(pseudo_R2_epds_unadj,3)` for the pupil‑only model and `r round(pseudo_R2_epds_adj,3)` for the full model including age and baseline EPDS (EPDS_T1). This indicates that pupil measures alone explain only a small proportion of the variability in later symptom thresholds, while the addition of demographic and prior symptom information substantially improves model fit.

```{r OR_tables, echo=FALSE, warning=FALSE, message=FALSE}

epds_pros_tbl <- tbl_regression(epds_pros, exponentiate = T, include = c(SPDD_T1, IPDD_T1), label =  list(SPDD_T1 ~ "SPDD (T1)", IPDD_T1 ~ "IPDD (T1)")) %>% 
  bold_labels() %>% 
  italicize_levels() 

gad_pros_tbl <- tbl_regression(gad_pros, exponentiate = T, include = c(SPDD_T1, IPDD_T1), label =  list(SPDD_T1 ~ "SPDD (T1)", IPDD_T1 ~ "IPDD (T1)")) %>% 
  bold_labels() %>% 
  italicize_levels()

tbl_pros <- tbl_stack(list(gad_pros_tbl, epds_pros_tbl), group_header = c("GAD-7 ≥ 7 (T2)", "EPDS ≥ 10 (T2)"))

tbl_pros <- tbl_pros %>% modify_header(groupname_col ~ "**Outcome**", label ~ "**Exposure**")

tbl_pros %>%
  as_flex_table() %>%
  save_as_docx(path = "tbl_pros.docx")

tbl_pros

```

```{r forest_plot, echo=FALSE, warning=FALSE, message=FALSE}

library(dplyr)
library(ggplot2)
library(mice)
library(broom.mixed)

# Extract and pool both models
get_or <- function(fit, model_name) {
  pooled <- pool(fit)
  tidy(pooled, conf.int = TRUE, exponentiate = TRUE) %>%
    filter(term %in% c("IPDD_T1", "SPDD_T1")) %>%
    mutate(model = model_name)
}

plot_data <- bind_rows(
  get_or(gad_pros, "GAD-7 ≥ 7 (T2)"),
  get_or(epds_pros, "EPDS ≥ 10 (T2)")
)

library(dplyr)
library(ggplot2)
library(ggtext)

# Prepare data for a clean two-panel look
plot_data_pub <- plot_data %>%
  mutate(
    term_name = case_when(
      term == "IPDD_T1" ~ "IPDD (T1)",
      term == "SPDD_T1" ~ "SPDD (T1)"
    ),
    model = factor(model, levels = c("GAD-7 ≥ 7 (T2)", "EPDS ≥ 10 (T2)"))
  )

# Professional plot
p <- ggplot(plot_data_pub, aes(x = estimate, y = term_name, color = model, shape = model)) +
  geom_vline(xintercept = 1, linetype = "solid", linewidth = 0.5, color = "black") +
  geom_point(size = 3.5, position = position_dodge(width = 0.6)) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), 
                 height = 0.3, linewidth = 0.8, position = position_dodge(width = 0.6)) +
  scale_x_log10(breaks = c(0.5, 1, 2, 4), labels = c("0.5", "1.0", "2.0", "4.0")) +
  scale_color_manual(values = c("#0072B2", "#D55E00")) + # Professional blue/orange
  labs(x = "Odds ratio (95% CI)", y = NULL, color = NULL, shape = NULL) +
  theme_classic(base_size = 14) +
  theme(
    legend.position = "bottom",
    axis.text = element_text(color = "black", size = 12),
    axis.line.y = element_blank(),
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.3)
  )

ggsave(
  filename = "forest_plot.tiff",
  plot = p,
  width = 6,
  height = 4,
  units = "in",
  dpi = 600,
  compression = "lzw"
)

p
```

**Figure [X].** Adjusted odds ratios for pupil indices at T1 predicting symptom thresholds at T2. Estimates are from logistic regression models for GAD-7 (≥ 7) and EPDS (≥ 10), with 95% confidence intervals indicated by horizontal bars. Reference line at OR = 1 indicates null effect.

# Sensitivity analysis
